### 2019-09-30 proglog.tex
adds mccarthy

\subsubsection{Todd Allen, UW Madison}
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-allen.jpeg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	His first post-Ph.D. position was as a staff scientist at Argonne National Laboratory. While at Argonne, he joined the leadership team tasked with developing the Generation IV Roadmap, the document that framed the resurgence of the nuclear research programs early in the 21st Century.Following Argonne, he joined the faculty at the University of Wisconsin. While there, he split his time between establishing a premier material science program at the university and supporting the Idaho National Laboratory. At INL, he led the transition of the Advanced Test Reactor into a national user facility. He also ran a six-institution Energy Frontier Research Center focused on answering fundamental questions about heat transfer in nuclear fuel.
From 2013-2016, he helped lead the Idaho National Laboratory as the Deputy Laboratory Director for Science $\&$ Technology, including being an important contributor to the development of the Gateway for Accelerated Innovation in Nuclear (GAIN) initiative announced at the White House in November 2015. Since 2016 he has been a Visiting Senior Fellow with Clean Energy Program at Third Way, a Washington, DC based think tank. His role in formulating the roadmap for Generation IV reactors and his leadership indicate that he would make a great speaker at the conference.
\end{minipage}

@@

% \clearpage
\subsubsection{Ross Radel, CEO Phoenix, LLC}
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-radel.png}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	Ross Radel is the CEO and a Board of Directors member of Phoenix. He holds a MS and a PhD in Nuclear Engineering from the University of Wisconsin-Madison. He previously worked as the Senior Member of the Technical Staff at Sandia National Laboratories. Ross has extensive experience with nuclear reactors and advanced power conversion systems that are directly applicable to Phoenix’s core technologies. His previous research at the University of Wisconsin focused on high-flux neutron generation for detecting clandestine material, specifically highly enriched uranium. The mission of Radel's company, Phoenix, is to transform nuclear technology to better our world. This mission statement reflects our mission in hosting the student conference well. We believe Dr. Radel would be a great speaker for the future of nuclear technology.
\end{minipage}

@@

\subsubsection{Applications for Plasma Processing}
Plasma processing has become a staple in many fields of advanced manufacturing. Without plasma, modern conveniences such as smartphones and powerful computer technology would not be possible. In this panel, representatives from companies at the cutting-edge of plasma processing research will discuss how plasmas continue to revolutionize contemporary industry. Potential panelists include Brian Jurczyk, CEO of Starfire Industries, and Phi Nguyen, former Vice President and Director of Engineering at Intel Corp.

>>>>

\subsubsection{Cathy McCarthy, Canadian Nuclear Laboratories}
\begin{minipage}{0.25\textwidth}
	\centering
	\includegraphics[width=\textwidth]{fmt-mccarthy.jpg}
\end{minipage}
\begin{minipage}{0.73\textwidth}
	Dr. Kathy McCarthy joined CNL as the Vice-President of Research and Development in 2017. Kathy has also held the position of Director of the US Department of Energy Light Water Reactor Sustainability Program Technical Integration Office. Her team, made up of scientists and engineers from across the US, conducted and guided important research that enabled power companies to be able to make informed decisions regarding long-term operation broadly, and second licence renewal specifically, for their operating nuclear units. Her expertise, leadership and contributions to the nuclear science and technology community are globally recognized, having received the American Nuclear Society Presidential Citation (2015, 2007), and the Partnership for Science \& Technology Nuclear Energy Advocate of the Year Award (2011), among many others. Her many contributions to the nuclear industry indicate that she would make a great speaker at this confrence. 
\end{minipage}

@@

% % \clearpage
% \subsubsection{Ross Radel, CEO Phoenix, LLC}
% \begin{minipage}{0.25\textwidth}
% 	\centering
% 	\includegraphics[width=\textwidth]{fmt-radel.png}
% \end{minipage}
% \begin{minipage}{0.73\textwidth}
% 	Ross Radel is the CEO and a Board of Directors member of Phoenix. He holds a MS and a PhD in Nuclear Engineering from the University of Wisconsin-Madison. He previously worked as the Senior Member of the Technical Staff at Sandia National Laboratories. Ross has extensive experience with nuclear reactors and advanced power conversion systems that are directly applicable to Phoenix’s core technologies. His previous research at the University of Wisconsin focused on high-flux neutron generation for detecting clandestine material, specifically highly enriched uranium. The mission of Radel's company, Phoenix, is to transform nuclear technology to better our world. This mission statement reflects our mission in hosting the student conference well. We believe Dr. Radel would be a great speaker for the future of nuclear technology.
% \end{minipage}

@@

\subsubsection{Plasma Processing in Your Pocket}
Plasma processing has become a staple in many fields of advanced manufacturing. Without plasma, modern conveniences such as smartphones and powerful computer technology would not be possible. In this panel, representatives from companies at the cutting-edge of plasma processing research will discuss how plasmas continue to revolutionize contemporary industry. Potential panelists include Brian Jurczyk, CEO of Starfire Industries, and Phi Nguyen, former Vice President and Director of Engineering at Intel Corp.
